### 2022-05-24 main/chapter_2ljets.tex
rename to features, add welcome, improve itemize

\section{Event variables}
% lepton, jet definitions

@@

In short, all triggers require $\pt^{\ell_i}$ values to exceed
$8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: symmetric requirements vary between
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$ and
\item $\pt^{\mu_2} > 14~\eV[G]$.
\end{itemize}
Asymmetric requirements vary between
\begin{itemize}
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}

>>>>

\section{Event features}
% lepton, jet definitions

From its name, the $\twoljets$ analysis analyses features of events with two
charged leptons (electrons or muons --- not taus), and at least one jet.
Though not nominal, the a $\met$ requirement is also implicit from the context
of $R$-parity conserving supersymmetric models.
This section serves to describe how events are selected for the $\twoljets$
analyses, and which event variables are extracted for use in its selections.

Triggers and object definitions are shared between the three $\twoljets$
searches.
Higher level event variables and selections will only be described for the
$\twoljets$ electroweak search.

@@

In short, all triggers require $\pt^{\ell_i}$ values to exceed thresholds in
the range $8\textrm{--}26~\eV[G]$.
To detail all trigger requirements and their variations with data period
would be too tedious and not enlightening, but their $\pt^{\ell_i}$ requirements
are summarized here.
\begin{itemize}
\item Electron pair: requirements vary between
\begin{itemize}
\item $\pt^{e_2} > 12~\eV[G]$ and
\item $\pt^{e_2} > 17~\eV[G]$.
\end{itemize}
\item Muon pair: various requirements include
\begin{itemize}
\item $\pt^{\mu_2} > 10~\eV[G]$,
\item $\pt^{\mu_2} > 14~\eV[G]$,
\item $\pt^{\mu_1} > 18~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$, and
\item $\pt^{\mu_1} > 22~\eV[G]~\&~\pt^{\mu_2} > 8~\eV[G]$.
\end{itemize}
\item Emu pair: various asymmetric requirements include
\begin{itemize}
\item $\pt^{e_1} > 17~\eV[G]~\&~\pt^{\mu_1} > 14~\eV[G]$,
\item $\pt^{e_1} > 7~\eV[G]~\&~\pt^{\mu_1} > 24~\eV[G]$, and
\item $\pt^{e_1} > 26~\eV[G]~\&~\pt^{\mu_1} > 8~\eV[G]$.
\end{itemize}
\end{itemize}
Trigger requirements have increased in hardness with time.
